\textsf{Are large language models superhuman chemists?}

### 2024-10-18 src/tex/appendix.tex
add variables

@@

@@

\begin{figure}
    \centering 
    \includegraphics{figures/process.pdf}
    \caption{\textbf{Overview of the benchmarking pipeline implemented in \chembench.} The process begins with JSON files containing task data, which are used to create \texttt{Task} objects and initialize the \texttt{ChemBenchmark}. \texttt{Prompter} objects are then created to handle different types of prompts for instruction-tuned and completion models.
    The \texttt{Task} Iterator differentiates between \gls{mcq} and other question types. For each task type, appropriate prompts are generated and passed to the \gls{llm}. The responses are then processed using regex-based parsing methods specific to \gls{mcq} or numeric answers (after obtaining the relevant part of the response from the instruction-tuned models). 
    The regex-based parsing is elaborate and also able to handle special cases such as scientific notation, or roman numerals.
    If the initial parsing is unsuccessful, the system employs an \gls{llm}-based extraction method as a fallback. The parsed or extracted answers then undergo metric computation and refusal detection.}
    \label{fig:process}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{figures/correlation_plot_is_electron_counts_num_atoms.pdf}
    \caption{\textbf{Dependence of the mean absolute error in predicting total electron counts on the number of atoms.} The plot shows that for the \glspl{llm}, the predictive performance (measured as the mean absolute error in the prediction of the total electron counts) is correlated with the number of atoms in the molecule.}
    \script{correlate_with_molecule_features.py}
    \label{fig:correlation_plot_is_electron_counts_num_atoms}
\end{figure}

>>>>

% \begin{figure}
%     \centering
%     \includegraphics[]{figures/cb_humanset_v1.pdf}
%     \caption{\textbf{Composition of the human subset.} The circular plot shows the distribution of topics and required skills in the human subset of the \chembench corpus. The human subset is a representative subset of the full corpus, with a balanced distribution of topics and skills.}
% \end{figure}

@@

\begin{table}
    \caption{\textbf{Performance of the models on the \chembench corpus.} The table shows the fraction of questions answered completely correctly by the models for different skills and difficulty levels.}
    \variable{output/performance_table.tex}
\end{table}

\begin{table}
    \caption{\textbf{Performance of the models on the \enquote{tiny} subset of the \chembench corpus.} The table shows the fraction of questions answered completely correctly by the models for different skills and difficulty levels.}
    \variable{output/performance_table_human_subset.tex}
\end{table}

@@

\begin{figure}
    \centering 
    \includegraphics[height=\textheight]{figures/process.pdf}
    \caption{\textbf{Overview of the benchmarking pipeline implemented in \chembench.} The process begins with JSON files containing task data, which are used to create \texttt{Task} objects and initialize the \texttt{ChemBenchmark}. \texttt{Prompter} objects are then created to handle different types of prompts for instruction-tuned and completion models.
    The \texttt{Task} Iterator differentiates between \gls{mcq} and other question types. For each task type, appropriate prompts are generated and passed to the \gls{llm}. The responses are then processed using regex-based parsing methods specific to \gls{mcq} or numeric answers (after obtaining the relevant part of the response from the instruction-tuned models). 
    The regex-based parsing is elaborate and also able to handle special cases such as scientific notation, or roman numerals.
    If the initial parsing is unsuccessful, the system employs an \gls{llm}-based extraction method as a fallback. The parsed or extracted answers then undergo metric computation and refusal detection.}
    \label{fig:process}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/correlation_plot_is_electron_counts_num_atoms.pdf}
    \caption{\textbf{Dependence of the mean absolute error in predicting total electron counts on the number of atoms.} The plot shows that for the \glspl{llm}, the predictive performance (measured as the mean absolute error in the prediction of the total electron counts) is correlated with the number of atoms in the molecule.}
    \script{correlate_with_molecule_features.py}
    \label{fig:correlation_plot_is_electron_counts_num_atoms}
\end{figure}
